Case study validations of automatic bullet matching

### 2018-11-21 index.Rmd
Not working yet, but try to fix draft behavior AND title page behavior

# to produce blinded version set to 1
blinded: 1

@@

```{r child-doc-compile, include = F, cache = F}
thisdoc <- readLines("index.Rmd")
idxs <- which(str_detect(thisdoc, "^---$"))
if (length(idxs) >= 2) {
  # Get yaml metadata, set to nonblinded, write to title-page.Rmd
  thisdoc[idxs[1]:idxs[2]] %>%
    str_replace("^blinded: 1", "blinded: 0") %>%
    str_replace("^abstract:.*", "") %>%
    writeLines(con = "title-page.Rmd")
}

@@

if (!dir.exists("separate_fig_files")) dir.create("separate_fig_files")
file.copy(figs$file, file.path("separate_fig_files", figs$fig_label))

>>>>

blinded: 1 # to produce blinded version set to 1
titlepage: 0 # This gets changed automatically when the title page is compiled in the chunk child-doc-compile
draft: 0 # Set to 1 if figures should be included with the text

@@

```{r child-doc-compile, include = F, cache = F}
thisdoc <- readLines("index.Rmd")
idxs <- which(str_detect(thisdoc, "^---$"))
if (length(idxs) >= 2) {
  # Get yaml metadata, set to nonblinded, write to title-page.Rmd
  thisdoc[idxs[1]:idxs[2]] %>%
    str_replace("^blinded: 1", "blinded: 0") %>%
    str_replace("^titlepage: 0", "titlepage: 1") %>%
    str_replace("^abstract:.*", "") %>%
    writeLines(con = "title-page.Rmd")
}

@@

if (!dir.exists("separate_fig_files")) dir.create("separate_fig_files")
file.copy(figs$file, file.path("separate_fig_files", figs$fig_label), overwrite = T)
